Character LSTM for Sentiment Analysis on Twitter

### 2015-12-21 paper/paper.tex
compiled pdf

\section{Introduction}
% why analysis sentiment expecially twitter
In the last few years, microblogging has become a very popular communication tool in people's social life. Microblogging platforms like Twitter and Facebook allow users to share their opinions on a wide variety of topics. This popularity results in enormous amount of information covering a wide range of topics on various brands, products, politics and social events.

Sentiment analysis on microblogging corpora has become an import area of research across the fields of NLP, machine learning, and social science research. 
Sentiment analysis on microblogging has obtained special interest, because it determines the attitude of a user with respect to some topic or product and thus provides convincing information of user's interest or feedback on the topic.

For example, it may help a consumer products company get relevant feedback of public opinion on a recent product launch.

>>>>

\section{Introduction}
% why analysis sentiment expecially twitter
In the last few years, microblogging has become a very popular communication tool in people's social life. Microblogging platforms like Twitter and Facebook allow users to share their opinions on a wide variety of topics. Users of these platforms generate enormous amount of information covering a wide range of topics on various brands, products, politics and social events.

Sentiment analysis on microblogging corpora has become an important area of research across the fields of NLP, machine learning, and social science research. 
Sentiment analysis on microblogging has obtained special interest, because it determines the attitude of a user with respect to some topic or product and thus provides convincing information of user's interest or feedback on the topic.
For example, it may help a consumer products company get relevant feedback of public opinion on a recent product launch.
